%If working on sections in "1.1 Architecture requirements" only use from subsection downwards

\subsection{Quality requirements}
	\subsubsection{Critical}
		\begin{itemize}
			\item Scalability: \\
			The system is expected to have a maximum of 2000 users as specified by the client. Buzz Space is meant to encourage discussions on multiple topics at the same time by a large amount of users so the system needs to be able to handle many concurrent users too.
			\item Maintenance and Audit-ability \\
			The system should be monitor-able and audit-able, to enable lecturers to monitor the discussion boards and to see who posted what on the Buzz Space. Lecturers should be able to evaluate and monitor each user to be able to give the user a participation mark for the discussion board. Lecturers should be able to prevent irrelevant posts and discussions and should be able to see who were part of the discussion and notify them that it has been removed and should then be able to give them a warning.
		\end{itemize}
	\subsubsection{Important}
		\begin{itemize}
			\item Usability \\
			The system must be as usable as possible so that users are encouraged to use it as much as possible. The extent to which the system can be made usable is affected by the priority of scalability and audit-ability because if the system is made scalable so that it can be used by all students at the same time, it is impossible to cater for 2000 student's needs and make it 100\% usable for the mass. Usability is marked important because the participation of students can be greatly affected if the system is unusable and students will then lose marks.

			\item Integrability \\
			One of the functional requirements was that the system be pluggable into other systems, this is why integrability is considered quite important. That means the system should be a collection of independent components. These components should be easily pluggable into other systems. The system itself should be able to seemlessly integrate other systems into it.
			\item Security \\
			Security is important because the evaluation of users' participation is involved. Not all of the users should be able to access these sensitive information and therefore certain users will be authorized to do certain actions, where other users will not be allowed to. The system should be able to authenticate users for data integrity. Only users who are registered to the Buzz Space get access and will be able to partake in the discussion boards. If the system is very secure, it will help to ensure Reliability and Availability.
		\end{itemize}