%If working on sections in "1.1 Architecture requirements" only use from subsection downwards

\section{Architectural patterns}
	\subsection{Loose Coupling}
		\subsubsection{Description}
		Loose coupled systems only allow accessing of resources through a proxy or accessing a pool of resources instead of a single resource. Loose coupling refers to the indirect access to external resources. 
		\subsubsection{Quality Requirements it enforces}
		\begin{itemize}
			\item Scalability \\
			This loose coupling of systems via APIs makes your application more scalable because systems can off-load part of your processing to other systems that are independently scalable. 
			\item Maintainability \\
			This loose coupling of systems via APIs makes your application more maintainable because bugs and problems are enclosed in the module and not in the system as a whole. 
			\item Integration \\
			Because loose coupled modules should work independent, its very easy to integrate a loose coupled system into another system by using an adapter module. 
			\item Security \\
			Because loose coupled modules are only accessed through the API, all databases/servers are only accessed by the module and not directly by the user.
		\end{itemize}	
			
	\subsection{Blackboard Pattern}
		\subsubsection{Description}
 By allowing multiple processes such as creating a root thread or rating a user to work closer together on different threads, polling and reacting if needed so that less time is wasted by running processes in parallel.
		\subsubsection{Quality Requirements it enforces}
		\begin{itemize}
			\item Scalability
It is easy to achieve scalability with the blackboard pattern accross a grid of processors subject to having a scalable implementation of the blackboard itsself.
		\end{itemize}	
		
	\subsection{Prototype pattern}
		\subsubsection{Description}
 			By deep cloning objects to store their data in the audit log if any changes occurred, without keeping a reference to the original data and exposing it.
		\subsubsection{Quality Requirements it enforces}
		\begin{itemize}
			\item Maintainability an Auditability
The prototype pattern makes clones of the old values(deep cloning) and then extracts the data needit in the audit trail.
			\item Security
Beacause the prototype pattern works on a sceleton based design in some sense it helps with security by limiting manipulation possibilities.

		\end{itemize}	