%If working on sections 1.2 to 1.6 only use from section downwards

\section{Strategies}
	\subsection{Scalability}
		\begin{itemize}
			\item Addition of system resources.
			\item Store data on client side for less traffic on server.
			\item Loose-coupling sub systems tied together by API's.
		\end{itemize}
	\subsection{Maintainability and Audit-ability}
		\begin{itemize}
			\item Model-View-Controller Strategy when approaching the user interface for easy maintenance.
			\item Use separate table for the audit log.
			\item Log all user Activity.
		\end{itemize}
	\subsection{Usability}
		\begin{itemize}
			\item Model-View-Controller Strategy when approaching the user interface.
			\item Use as many as possible known icons and symbols to bridge the language barrier.
			\item Usability testing by asking non tech-savvy individuals to use the system.
		\end{itemize}
	\subsection{Integrability}
		\begin{itemize}
			\item Using a separate adapter class/model to make the system.
			\item Loose-coupling sub systems tied together by API's to allow easy access from other systems through the API's.
			\item Using the prototype pattern to create the default database layout with regards to your configuration. specifications
		\end{itemize}
	\subsection{Security}
		\begin{itemize}
			\item Model-View-Controller Strategy when approaching the user interface.
			\item Loose-coupling sub systems tied together by API's to limit access only to the allowed API calls.
			\item Security testing by running a hacking challenge on the system.
		\end{itemize}