\documentclass[12pt, a4paper]{article}
\begin{document}
\title{Quality Requirements(Middle 3)}
\author{Shaun Meintjes}
\maketitle
\pagebreak

\tableofcontents
\pagebreak

\section{Quality Requirements}
\subsection{Reliability and Availability - Important}
Reliability and Availability is important in our system, as maintainability will then be less needed in an ideally reliable system. One of the key features of a discussion board is that it should be available 24/7. Users want answers and help as soon as possible, and therefore the system should be reliable and available at all times. If the system is very reliable and available, discussions that are of a time essence can be seen to as soon as possible. Reliability can be defined as the probability that a system will produce correct outputs up to some given time. A reliable system does not silently continue and deliver results that include uncorrected corrupted data. Availability means the probability that a system is operational at a given time. A highly available system would disable the malfunctioning portion and continue operating at a reduced capacity. \\

If the system is very reliable and available, users will be able to use the system with ease and the users will trust the Buzz system.


\subsection{Security - Important}
Security is important because the evaluation of users' participation is involved. Not all of the users should be able to access these sensitive information and therefore certain users will be authorized to do certain actions, where other users will not be allowed to. Only users who are registered to the Buzz Space gave access and will be able to partake in the discussion boards. If the system is very secure, it will help to ensure Reliability and Availability.

\subsection{Monitorability and Auditability - Critical}

The system should be monitorable and auditable, to enable lecturers to monitor the discussion boards and to see who posted what on the Buzz Space. Lecturers should be able to evaluate and monitor each user to be able to give the user a participation mark for the discussion board.  Lecturers should be able to prevent irrelevant posts and discussions and should be able to see who were part of the discussion and notify them that it has been removed and should then be able to give them a warning.\\

 This can all be achieved by ensuring that the system is monitorable and auditable.

\end{document}